---
title: "Case Study 2 Wealth and Life Expectancy (Gapmiinder)"
author: "Nathan Ackley"
date: "5/2/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(gapminder)
View(gapminder)

noku <- filter(gapminder, country != "Kuwait")
```

## Background

I wasn't aware of the facet_wrap function, which is super useful for creating multiple graphs in the same row. I also wasn't aware that you could create a "group" in the geom_line function to group your lines by a specific variable. I know I didn't do the second graph perfectly, but it will only push me to learn more about ggplot and the tidyverse in general.

```{r}
p <- ggplot(noku) +
  theme_bw() +
  geom_point(mapping = aes(x = lifeExp, y = gdpPercap, size = pop, color = continent)) +
  facet_wrap( ~ year, nrow = 1) +
  scale_y_continuous(trans = "sqrt")

p


ggsave("plot_1", device = "png", width = 15)
```

## Including Plots

You can also embed plots, for example:

```{r}
h <- ggplot(noku, aes(x = year, y = gdpPercap, color = continent)) +
  theme_bw() +
  geom_point() +
  geom_line(aes(group = country)) +
  ylim(0 , 50000) +
  facet_wrap(~continent, nrow = 1) +
  scale_y_continuous(trans = "sqrt") +
  geom_line(data = k, aes(x = year, y = GDP, color = "black")) +
  geom_point()
  ggsave("plot_2", device = "pdf", width = 15)

  h 
  
#k <- noku %>% 
#+ group_by(continent, year) %>% 
#+ summarise(GDP = weighted.mean(gdpPercap))  
  
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
